---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mercedestrenzr

<!-- badges: start -->
<!-- badges: end -->

The goal of mercedestrenzr is to inspect and analyze used Mercedes Benz car prices. The package helps users to get simple answers on how to choose the used Mercedes Benz car in the market. The package also includes useful visualization tool and trained model to serve buyers and sellers.

## Installation

You can install the development version of mercedestrenzr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("UBC-MDS/mercedestrenzr")
```

## Example (TO BE COMPLETED once the function codes are added)

This is a basic example which shows you how to solve a common problem:

```{r example}
#library(mercedestrenzr)
## basic example code

# load sample data from package

# filter listings based on budget range of characteristics of interest
#listing_search(data, budget=c(0, 30000), model = "any", sort_feature = "odometer", ascending = TRUE)

# visualizing the price distribution

# predict how much a car would be using regression model

```


